Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-25 DGMM2025/normalsandcurvature.tex
legend fixing + adjusted trendlines
paragraph Experimental validation

\paragraph{Experimental validation.} [TO COMPLETE]
Figure~\ref{fig:normals-estimation} shows an example
of our normals compared to normals computed with the integral invariant (II) estimator~\cite{Lachaud:2017-lnm}.

@@

                ] {0.1*x^(0.5)};

@@

                ] {0.1*x^(0.5)};

@@

            \addlegendimage{color=black,thick};
            \addlegendentry{$0.1\sqrt{h}$}
                \end{axis}
            \end{tikzpicture}
        } \\
    \end{tabular}
    \caption{Error RMSE and $E_{\max}$ as a function of grid resolution}
    \label{fig:errors-normals}
\end{figure}

>>>>

\paragraph{Experimental validation.}
Figure~\ref{fig:normals-estimation} shows an example
of our normals compared to normals computed with the integral invariant (II) estimator~\cite{Lachaud:2017-lnm}.
In order to compare quantitatively the different normal estimators, we compute the
root mean square error (RMSE) and the maximum error $E_{\max}$ of the
normals computed on a digital surface with respect to the normals computed
on the continuous surface. We use 4 different digital surfaces (ellipsoid,
goursat, rcube and sphere9). We see that the RMSE and $E_{\max}$ errors of our
estimator are convergent with respect to the grid resolution with a
rate of convergence of $h^{\frac{2}{3}}$ for the RMSE and $h^{\frac{1}{2}}$ for
$E_{\max}$.

@@

                ] {0.1*x^(0.66)} node[pos=0.2, anchor=south west] {$h^{\frac{2}{3}}$};

@@

                ] {0.1*x^(0.5)} node[pos=0.5, anchor=north east] {$h^{\frac{1}{2}}$};

@@

                \end{axis}
            \end{tikzpicture}
        } \\
    \end{tabular}
    \caption{Error RMSE and $E_{\max}$ as a function of grid resolution}
    \label{fig:errors-normals}
\end{figure}
